\documentclass[11pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}

\begin{document}
\begin{center}
    \huge \textbf{THANG LE}\\
    \hrulefill
\end{center}

\begin{center}
    Cau Giay, Ha Noi \textbullet \ lethang1281@gmail.com \textbullet \ 0981779204
    \textbullet \ lethang-shopeeap.vercel.app
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{University of Engineering and Technology - VNU} \hfill Cau Giay, Ha Noi

Computer Science Bachelor | Data Analyst \hfill est. 06/2026
\vspace{12pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{ECOMUP} \hfill Hanoi

\textbf{Growth \& Business Development} \hfill 01/2026 -- Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Research and evaluate product opportunities across categories by analyzing market trends, competitor positioning, and customer demand to inform category expansion decisions.
    \item Drive seller-side growth by identifying high-potential product lines, coordinating go-to-market launches, and aligning cross-functional teams on revenue targets.
    \item Build and maintain data dashboards to monitor category performance (revenue, margins, conversion rates), translating insights into actionable growth strategies.
\end{itemize}
Key Skills: Product Research, Category Growth, Go-to-Market, Data Analytics, Cross-functional Coordination

\vspace{12pt}

\textbf{Tai Chinh Xanh JSC.} \hfill Ha Noi

\textbf{E-commerce Operations \& Growth} \hfill 09/2025 -- 12/2025
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Managed day-to-day e-commerce operations for the ``Softie'' brand, keeping marketing, operations, and finance teams aligned on business priorities and growth targets.
    \item Coordinated with creative and marketing teams to plan and execute promotional campaigns, managing daily budgets and iterating on underperforming initiatives to improve ROI.
    \item Analyzed sales and operational reports to identify cost-reduction and revenue-growth opportunities, feeding findings directly into strategic planning.
\end{itemize}
Key Skills: E-commerce Operations, Cross-functional Coordination, Revenue Analysis

\vspace{12pt}

\textbf{NextStart Incubator - NextTech} \hfill Ha Noi

\textbf{Batch-1 Member - Growth \& Business Development} \hfill 06/2025 -- 10/2025
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Conducted market research and competitive analysis for D2C product concepts, validating demand and identifying target audience segments before go-to-market.
    \item Developed go-to-market strategies and pitched growth plans to mentors and industry experts, receiving selection into the inaugural cohort.
    \item Collaborated across product, marketing, and tech teams to align business development efforts with customer acquisition goals.
\end{itemize}
Key Skills: Market Research, Go-to-Market Strategy, Business Development, D2C

\vspace{12pt}

\textbf{Thinkmay CO.,LTD} \hfill Ha Noi

\textbf{Growth Analyst} \hfill 06/2025 -- 09/2025
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Worked directly with the CEO to define growth priorities and align business initiatives with market positioning goals.
    \item Conducted user research and landing page analysis to identify friction points and improve conversion rates.
    \item Managed content and campaign planning from concept to execution, with a focus on user acquisition and engagement.
\end{itemize}
Key Skills: Growth Strategy, User Research, Stakeholder Management

\newpage
\begin{center}
    \textbf{Skills \& Competencies}
\end{center}

\textbf{Business Development \& Growth Strategy}

\textbf{Market Research, Category Growth, Go-to-Market Planning, Seller Acquisition}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Research market trends, competitor landscapes, and customer segments to identify growth opportunities and validate new product or category launches.
    \item Develop and execute go-to-market strategies spanning product selection, positioning, and cross-functional coordination.
    \item Experience working with sellers and product teams to drive category expansion and revenue growth in e-commerce.
\end{itemize}

\vspace{8pt}

\textbf{E-commerce Operations \& Platform Knowledge}

\textbf{Marketplace Operations, Cross-functional Coordination, Process Improvement}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Operated e-commerce businesses end-to-end: product sourcing, storefront management, fulfillment coordination, and margin optimization.
    \item Coordinated across marketing, operations, and finance teams to keep business growth on track.
    \item Understand e-commerce fulfillment workflows and how operational decisions affect customer experience and profitability.
\end{itemize}
\vspace{8pt}

\textbf{Data Analysis \& Decision Making}

\textbf{Dashboards, Business Reporting, Data-driven Strategy}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Built reports combining revenue, cost, and operational data to inform strategic decisions on category and seller growth.
    \item Interpreted business data to identify trends, flag opportunities, and support stakeholder decision-making.
    \item Used AI tools (Claude, Cursor) to accelerate data processing and insight generation.
\end{itemize}

\vspace{12pt}


\begin{center}
    \textbf{Certificates}
\end{center}

\textbf{English Proficiency -} IELTS 7.0 (2022)

\textbf{Market Research \& Business Ideation -} NextTech \& Agile Academy (2025)

\textbf{Scrum Essence 2.0 -} Agile Academy (2025)

\textbf{Project Management -} Agile Academy (2025)

\vspace{12pt}
\begin{center}
    \textbf{Additional Information}
\end{center}
\textbf{Portfolio:} lethang-shopeeap.vercel.app

\textbf{Github:} github.com/thnglee

\textbf{Linkedin:} linkedin.com/in/thang-lee-75365a258/


\end{document}
